---
title: "ASSESSMENT 1 PART B"
author: "SHEERIN KAUR S4644440"
date: '2022-03-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
install.packages("readr")

```



```{r}
fastfood<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

fastfood%>%filter(calories>1000)

fastfood%>%arrange(desc(total_fat>40))



```
# add a new variable dont_eat_this which is high fat consumption
```{r}
fastfood%>%arrange(total_fat)%>%
arrange(desc(total_fat>40))%>%
  select(total_fat)



#if total calories is more than 500 than 'heavy_food' is high,
#if total calories is less than 250 than 'heavy_food" is low 
 # otherwise it is average for all other cases


fastfood%>%
  mutate(
    heavy_food=case_when(calories>500~"high",
                         calories<250~"low",
                         T~"average")
    
  )
  
    

```

8. Display the observations that has more than 1000 calories

9. Arrange observations with more than 40 in total_fat and more than 80 in total_carb in the descending order (PLEASE USE THE VARIABLE OF YOUR CHOICE TO ORGANISE THE DESCENDING ORDER) and save them to a new variable (dataset) called `dont_eat_this`

10. Using the initial dataset variable, use `case_when()` to create a new variable `heavy_food` which is equal to "heavy" when total calories are greater than 500, "low" when total calories are less than 250 and "average" for all other cases. Count the number of observations in each created category.

11. Display the types of variables in the dataset using `skimr` package 

12. Present the count observations from each restaurant in a descending order

Show the number of distnct items on a menu in the dataset

13. Using groupings (group_by()), summarise and display the average number of calories for each restaurant.

14. Add variables to the dataset, which:

-  calculates the average calories per type of restaurant and call it `average_calories` 
-  calculates the maximum total_fat per type of restaurant and call it `max_fat` 
-  calculates the minimum cholesterol per type of restaurant and call it `min_cholesterol` 

15. Display the data vis of total fat per each type of restaurant. Write a narration (2-3 sentences) why you believe this type of data viz presents such information best. 

16. Add a variable to the dataset, which calculates the sum of cholesterol and sodium and call it `cholesterol_sodium`.

Remove the variable `salad`

17. Use observations for Mcdonalds to plot sugar variable against protein with `geom_point()`