---
title: "ASSESSMENT 1"
author: "SHEERIN KAUR S4644440"
date: '2022-03-03'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## R MARKDOWN EDITING

Creating documents with **R Markdown** starts with an .Rmd file that contains a combination of markdown (content with simple text formatting) and **R code chunks**. The .Rmd file is fed to knitr, which executes all of the R code chunks and creates a new markdown (.md) document which includes the R code and its output.

The markdown file generated by knitr is then processed by pandoc which is responsible for creating a finished *web page*, PDF, *MS Word document*, *slide show*, *handout*, *book*, *dashboard*, *package vignette or other format*.

 https://rmarkdown.rstudio.com/lesson-8.html
 
 [**R MARKDOWN**](https://rmarkdown.rstudio.com/lesson-8.html)


You will need to *answer* each task using the text/graph narration and include R chunks to show how you get them.

2 Create the heading of the first level and call it RMarkdown editing 

3. Write 2-3 sentences about RMarkdown (you can google this information or use resources recommended in class - no need to reference)

4. In the above use bold and italics for editing. 

5. Review the suggested documentation on how to insert links in the .rmd file and include an in-text link to https://rmarkdown.rstudio.com/lesson-8.html 

 Insert an R chunk and create a variable with this dataset
https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv

The name of the variable should be `fastfood`

7. Display the first 10 rows of the dataset using head() and kable(). 

Display the first 10 rows of the dataset and the first 5 variables

Use Help and the link below to read more about those functions  https://bookdown.org/yihui/rmarkdown-cookbook/kable.html




```{r}

fastfood<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

fastfood%>%head(10)

knitr:: kable(fastfood[1:10, 1:5])

fastfood%>%select(calories,cal_fat,total_fat,sat_fat,trans_fat)




```






```










