---
title: "WORKSHOP 3 (THIRD CLASS)" nd work shop four tidy verse/ data wrangling
author: "KAUR"
date: '2022-03-01'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## data wrangling



```{r}
survey<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-05-18/survey.csv")

country<-survey%>%
  distinct(country)


survey%>%count(country,sort=TRUE)

survey_short<-survey%>%
  filter(
    country=="United States" |
      country=="USA" | 
      country=="US" | 
      country=="U.S." | 
      country=="United States of America" |
      country=="Usa"
    )


survey_short%>%filter(annual_salary>50000 & gender=="Woman")

survey_short%>%select(how_old_are_you, industry,annual_salary,gender)%>%
  filter(gender=="Woman")%>%filter(industry=="education")
```

arranging observations
```{r}
survey_short%>%top_n(n=10)


survey_short%>%arrange(desc(annual_salary))%>%
  select(industry, annual_salary)

survey_short%>%count(industry,sort=TRUE)

```

GROUPPINGS AND NEW VARIABLES
```{r}

survey_short%>%
  mutate(total_salary=annual_salary+other_monetary_comp)%>%
  select(industry,total_salary,annual_salary,other_monetary_comp)


survey_short%>%
  mutate(average_salary=mean(annual_salary, na.rm=TRUE))%>%
  select(industry, average_salary)
survey_short%>%
  group_by(industry)%>%
  mutate(average_salary=mean(annual_salary, na.rm=TRUE))%>%
           select(industry, average_salary)%>%
           arrange(desc(average_salary))%>%
           ungroup()
           
```

# add a new variable max_salary which is maximum salary per industry 
```{r}
survey_short%>%
  group_by(industry)%>%
  mutate(min_salary=min(annual_salary, na.rm=TRUE))%>%
           select(industry, min_salary)%>%
           arrange(desc(min_salary))%>%
           ungroup()
```

survey_short%>%
  group_by(industry, gender)%>%
  mutate(average_salary=mean(annual_salary, na.rm=TRUE))%>%
           select(industry, gender, average_salary)%>%
           arrange(desc(average_salary))%>%
           ungroup()
```{r}

survey_short%>%
  group_by(industry, gender)%>%
  mutate(average_salary=mean(annual_salary, na.rm=TRUE))%>%
           select(industry, gender, average_salary)%>%
           arrange(desc(average_salary))%>%
           ungroup()

```
summarising data 

```{r}

survey_short%>%
  group_by(industry)%>%
summarise(average_salary=mean(annual_salary,na.rm=TRUE))

```



```{r}
survey_short%>%
  group_by(industry)%>%
summarise(average_salary=mean(annual_salary,na.rm=TRUE))
```

```{r}
survey_short%>%
  group_by(gender,industry)%>%
summarise(average_salary=mean(annual_salary,na.rm=TRUE))
```

case_when
```{r}
survey_short_veryshort<-survey_short%>%
  select(industry, gender,annual_salary)

#if annual_salary is more than 700000 than your annual_salary_level is high, otherwise it is low 


survey_short_veryshort%>%
  mutate(
    annual_salary_level=case_when(annual_salary>700000~ "high", T~"loW")
    
    
  )%>%arrange(desc(annual_salary))
```
#if annual_salary is more than 700000 than your annual_salary_level is high, 
# if annual_salaryis more than 700000 but lessor equal to700000 then your annual_salary-level is middle 
#otherwiseit is low 

```{r}

survey_short_veryshort%>%
  mutate(
    annual_salary_level=case_when(annual_salary>700000~ "high",
                                  annual_salary>700000& annual_salary<=700000~"middle",
                                  T~"loW")
     )%>%arrange(desc(annual_salary))
```
#create variable highly_paid_women
#if gender=="Woman" and annual_salary>50000 then (~)it is "high, otherwise itis low 

```{r}
survey_short_veryshort%>%
  mutate(
    highly_paid_women=case_when(
      gender=="Woman"& annual_salary>50000~ "high", 
                                   
                                  T~"loW")
     )%>%arrange(desc(annual_salary))
```

